### 2015-07-05 narrative/qos.tex
more edits.

\subsubsection{Resource Management}
{\bf {\color{red} This section will be merged into the QoS - Gary}}
Sirocco currently offers automatic resource management capabilities. However,
these features are strictly driven on resource capacity and data resilience
requirements. For this project, we seek to expand the resource management
capabilities to support additional metrics to guide resource management
decisions. Our basic goal is to offer data-centric metrics that help guide the
forced resource management decisions.

@@

Existing efforts on scheduing resources~\cite{io-cop,dorier} attempt to offer
admission control to maximize storage performance. Unfortunately, these efforts
are limited to participating applications and only applications from a single
platform. For this approach to be effective, the storage system must offer an
approach that handles clients from all connected platforms and does not
require modification to use new storage access APIs. By using a priority
tagging system, we will offer defaults suitable for all applications that can
be informed by simple extensions to the job scheduler or more advanced
management through new APIs.

\paragraph{Related Work:}

>>>>

To achieve effective performance isolation, we seek to expand the resource management
capabilities in Sirocco to support additional metrics to guide resource management
decisions. Currently Sirocco offers automatic resource management capabilities,
based on resource capacity and data resilience requirements. 
 Our basic goal is to offer data-centric metrics that help guide the
forced resource management decisions.

@@

\paragraph{Related Work:} Existing efforts on scheduing resources~\cite{io-cop,dorier} attempt to offer
admission control to maximize storage performance. Unfortunately, these efforts
are limited to participating applications and only applications from a single
platform. For this approach to be effective, the storage system must offer an
approach that handles clients from all connected platforms and does not
require modification to use new storage access APIs. By using a priority
tagging system, we will offer defaults suitable for all applications that can
be informed by simple extensions to the job scheduler or more advanced
management through new APIs.
